Intro Seminar

### 2017-03-21 doc/seminar2017.Rmd
Used regression for continuous variables

# Box plot of uVDBP in different albuminuria categories
ds %>% 
  filter(fVN == "Baseline") %>% 
  select(acrStatus, udbpCrRatio) %>%
  na.omit() %>%
  box_plot_slides("acrStatus", "log(udbpCrRatio)", 
            "Albuminuria",
            "log uVDBP:Creatinine")

@@

ds %>% 
  filter(fVN == "Baseline") %>% 
  select(ACR, udbpCrRatio) %>% 
  na.omit() %>% 
  scatter_plot("log(ACR)", "log(udbpCrRatio)",
               "log Albumin:Creatinine Ratio",
               "log UDBP:Creatinine",
               line = TRUE)

@@

ds %>% 
  filter(fVN == "Baseline") %>% 
  select(eGFRStatus, udbpCrRatio) %>% 
  na.omit() %>% 
  box_plot_slides("eGFRStatus", "log(udbpCrRatio)", 
            "Estimated GFR (ml/min/1.73m^2)",
            "log uVDBP:Creatinine")

@@

ds %>% 
  dplyr::filter(!(eGFR_status == "Moderate")) %>% 
  dplyr::filter(eGFR < 150) %>% 
  dplyr::select(eGFR, udbpCrRatio) %>% 
  na.omit() %>% 
  scatter_plot("eGFR", "log(udbpCrRatio)",
               "Estimated Glomerular Filtration Rate (ml/min/1.73m^2)",
               "log UDBP:Creatinine") +
  ggplot2::geom_smooth(method = lm, colour = "grey50")

@@

ds %>% 
  filter(!(acrStatus == "Macroalbuminuria")) %>% 
  cor.test(formula = ~ eGFR + udbpCrRatio, data = ., method = "spearman")
```

@@

## Glycemic Status

```{r DM boxplot}

# Boxplot of uVDBP concentrations across DM categories

ds %>% 
  filter(fVN == "Baseline") %>% 
  select(dmStatus, udbpCrRatio) %>% 
  na.omit() %>% 
  box_plot_slides("dmStatus", "log(udbpCrRatio)", 
            "Glycemic Status",
            "log uVDBP:Creatinine")

## Vitamin D

```{r VitD scatterplot}

ds %>% 
  dplyr::filter(fVN == "Baseline") %>% 
  dplyr::select(VitaminD, udbpCrRatio) %>% 
  scatter_plot("log(udbpCrRatio)", "VitaminD",
               "log UDBP:Creatinine",
               "Serum 25(OH)D",
               line = TRUE)

ds %>% 
  dplyr::filter(fVN == "Baseline") %>% 
  cor.test(formula = ~ udbpCrRatio + VitaminD, data = ., method = "spearman")
```

>>>>

# Box plot of uVDBP in different albuminuria categories
ds %>% 
  filter(fVN == "Baseline") %>% 
  select(acrStatus, udbpCrRatio) %>%
  na.omit() %>%
  box_plot_slides("acrStatus", "log(udbpCrRatio)", 
            "Albuminuria",
            "log uVDBP:Creatinine (ug/mmol)")

@@

ds %>% 
  filter(fVN == "Baseline") %>% 
  select(ACR, udbpCrRatio) %>% 
  na.omit() %>% 
  scatter_plot("log(ACR)", "log(udbpCrRatio)",
               "log Albumin:Creatinine (mg/mmol)",
               "log uVDBP:Creatinine (ug/mmol)",
               line = TRUE)

@@

ds %>% 
  filter(fVN == "Baseline") %>% 
  select(eGFRStatus, udbpCrRatio) %>% 
  na.omit() %>% 
  box_plot_slides("eGFRStatus", "log(udbpCrRatio)", 
            "Estimated GFR (ml/min/1.73m^2)",
            "log uVDBP:Creatinine (ug/mmol)")

@@

ds %>% 
  # dplyr::filter(eGFR < 150) %>% 
  dplyr::filter(fVN == "Baseline") %>% 
  dplyr::select(eGFR, udbpCrRatio) %>% 
  na.omit() %>% 
  scatter_plot("eGFR", "log(udbpCrRatio)",
               "Estimated Glomerular Filtration Rate (ml/min/1.73m^2)",
               "log UDBP:Creatinine (ug/mmol)")

@@

ds %>% 
  # filter(!(acrStatus == "Macroalbuminuria")) %>% 
  dplyr::filter(fVN == "Baseline") %>% 
  cor.test(formula = ~ eGFR + log(udbpCrRatio), data = ., method = "spearman")

```{r glm}

# Multiple Regression -------------------------------------------

ds %>%
  dplyr::filter(fVN == "Baseline") %>% 
  # dplyr::mutate(UDBP = UDBP/1000) %>%
  dplyr::arrange(SID, VN) %>%

  mason::design("glm") %>% 
  mason::add_settings(family = stats::gaussian()) %>% 
  mason::add_variables("yvars", "UDBP") %>% 
  mason::add_variables("xvars", c("ACR", "eGFR")) %>% 
  mason::construct() %>% 
  # mason::add_variables("covariates", c("DM", "MedsBloodPressure")) %>% 
  # mason::construct() %>% 
  mason::add_variables("yvars", "VitaminD") %>% 
  mason::add_variables("xvars", "UDBP") %>% 
  mason::construct() %>% 
  mason::scrub()

@@
